---
title: "mini_beamer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mini_beamer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(miniBeamer)
library(rmarkdown)
```


# Introduction to mini_beamer

If u ever want to create a MiNI WUT themed presentation or business card the miniBeamer package makes it fast and easy.

This document introduces you to miniBeamer's basic set of tools, and shows you how to use them.

All sample presentations are available on GitHub.

### Create a PDF presentation from rmd file with rmd_to_beamer()

There are a number of parameters you can pass to the function to make your presentation look just the way you like.

```{r eval = FALSE}
rmarkdown::render('tests/prezentacja/prezentacja_pakietu.Rmd', 
                  miniBeamer::rmd_to_beamer(toc = TRUE,
                                           latex_engine = 'pdflatex',
                                           themecolor = 'white',
                                           fontcolor = 'black',
                                           bl = "/tests/prezentacja/logoPW.jpg",
                                           br = "/tests/prezentacja/logoMINI.png"))
```

### Create a PDF presentation from rnw file with  

You simply need to convert rnw file to rmd and then just use rmd_to_beamer on  the new file.

```{r eval = FALSE}
oldWd <- getwd()
newWd <- paste(getwd(), "/tests/rnw_to_rmd", sep="")
setwd(newWd)

miniBeamer::rnw_to_rmd('rnwExample.Rnw')
rmarkdown::render('rnwExample.Rmd', 
                  miniBeamer::rmd_to_beamer(toc = TRUE,
                                            latex_engine = 'pdflatex',
                                            themecolor = 'sapphire',
                                            fontcolor = 'graphite',
                                            bl = "C:/Users/Adam/Desktop/logoPW.jpg",
                                            br = "C:/Users/Adam/Desktop/logoMini.png"))

setwd(oldWd)
```

### Create a business card from rmd template

```{r eval = FALSE}
rmarkdown::render('tests/business_card/business_card.Rmd', miniBeamer::business_card())
```